Musical Deep Learning

### 2021-06-01 papers/final/jack/paper.tex
separate final paper to individual

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

@@

>>>>

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Nhut Minh Phan}
\email{phan92@uw.edu}
\affiliation{%
  \institution{University of Washington}
  \city{Bothell}
  \state{WA}
  \country{USA}
}

@@

Modelling raw audio waveforms is challenging since a single second in
modern recording spans thousands of timesteps. Most commonly music is
recorded at 44.1 kHz (44,100 samples per second). Since a piece of music
is at least a few seconds in length, capturing long-range dependencies
is difficult in time domain. A model named MelNet was introduced to address
this limitation of time-domain models \cite{vasquez2019melnet}. MelNet 
leverages a two-dimentional time-frequency representation of audio called 
spectrogram, which reduces the dimentionality of the audio waveforms. This 
model was able to generate high-fidelity audio samples using structures at 
long time scales.
